---
title: "QMM Module 4"
author: "Aman"
date: "2024-09-21"
output: html_document
---


#Installing Package lpsolve
```{r}

library(lpSolve)
```

```{r}
## Coefficients of the objective function (profit per unit)
profit <- c(420, 360, 300, 420, 360, 300, 420, 360, 300)
print(profit)
```

#Constraints for the coefficient 

# Production capacity constraints
```{r}
prod_cap <- matrix(c(
  1, 1, 1, 0, 0, 0, 0, 0, 0,   # Plant 1
  0, 0, 0, 1, 1, 1, 0, 0, 0,   # Plant 2
  0, 0, 0, 0, 0, 0, 1, 1, 1    # Plant 3
), nrow = 3, byrow = TRUE)

print(prod_cap)

```

## Storage constraints
```{r}
storage <- matrix(c(
  20, 15, 12, 0,  0,  0,  0,  0,  0,  # Plant 1
   0,  0,  0, 20, 15, 12,  0,  0,  0,  # Plant 2
   0,  0,  0,  0,  0,  0, 20, 15, 12  # Plant 3
), nrow = 3, byrow = TRUE)

print(storage)
```

## Sales constraints
```{r}
sales <- matrix(c(
  1, 0, 0, 1, 0, 0, 1, 0, 0,  # Large size
  0, 1, 0, 0, 1, 0, 0, 1, 0,  # Medium size
  0, 0, 1, 0, 0, 1, 0, 0, 1   # Small size
), nrow = 3, byrow = TRUE)

print(sales)
```


## Equal capacity usage constraint(Percentage constraints)
```{r}
capacity_equal <- matrix(c(
  1/750, 1/750, 1/750, -1/900, -1/900, -1/900, 0, 0, 0,
  0, 0, 0, 1/900, 1/900, 1/900, -1/450, -1/450, -1/450
), nrow = 2, byrow = TRUE)

print(capacity_equal)
```


## Combine all constraints

```{r}
constraints <- rbind(prod_cap, storage, sales, capacity_equal)

```

## Right-hand-side of constraints
```{r}
rhs <- c(750, 900, 450, 13000, 12000, 5000, 900, 1200, 750, 0, 0)
print(rhs)
```

## Directions of constraints
```{r}
dir <- c("<=", "<=", "<=", "<=", "<=", "<=", "<=", "<=", "<=", "=", "=")
```

## Solving the linear program
```{r}
solution <- lp("max", profit, constraints, dir, rhs)
print(solution)
```

## Decision variables (Production quantities)
```{r}
solution$solution  # Optimal production plan
```

# Objective Function value (Maximum profit:)
```{r}
print(solution$objval)    # Maximum profit
```



#Summary 

##Let X be the number of unit sized produced by the plants 
```{r}
# X11, X12, X13 = Production of large, medium, small units at plant 1.
# X21, X22, X33 = Production of large, medium, small units at plant 2.
# X31, X32, X33 = Production of large, medium, small units at plant 3.
```

$Max Z = 420(X11+X12+X13) + 360(X21+X22+X23)+300(X31+X32+X33)$

#Capacity Constraints:

$X11+X12+X13≤750$

$X21+X22+X23≤900$

$X31+X32+X33≤450$

#Storage Constraints:

$20X11+15X12+12X13≤1300$

$20X21+15X22+12X23≤1200$

$20X31+15X32+12X33≤5000$

#Demand Constraints:

$X11+X12+X13≤900$

$X21+X22+X23≤1200$

$X31+X32+X33≤750$

#Percentage Constraints:

$Plant 1: X11+ X12 +X13/750$

$Plant 2: X21+ X22 +X23/900$

$Plant 3: X31+ X32 +X33/450$

$X11+ X12 +X13/750 = X21+ X22 +X23/900$ 

$X21+ X22 +X23/900 = X31+ X32 +X33/450$

#We can simplify the equation into-

$900(X11+X12+X13)=750(X21+X22+X23), 450(X21+X22+X23)= 900(X31+X32+X33)$

#Non-negativity Constraint:
$X≥0$
